--- 
title: "Objective II"
author: "Daniel Rodriguez Duque"
site: bookdown::bookdown_site
---

# Simulation II Main Paper

Placeholder


## Value Function
## Matern 5/2 (n=500)
### Estimated Value Function
### Interpolating
### Homoskedastic
### Heteroskedastic

<!--chapter:end:index.Rmd-->


# Simulation III Main Paper

Placeholder


## Value Function
## Matern 5/2 (n=500)
### Estimated Value Function 
### Interpolating
### Homoskedastic
### Heteroskedastic

<!--chapter:end:01-SimulIII_Main.Rmd-->


# Simulation II Appendix

Placeholder


## Matern 5/2 (n=1000)
### Estimated Value Function 
### Interpolating
### Homoskedastic
### Heteroskedastic
## Matern 5/2 Heteroskedastic (n=1000)
### Estimated Value Function
### Interpolating Model
### Homoskedastic Model 
### Heteroskedastic Model
### Residuals
## Matern 3/2 (n=1000)
### Interpolating
### Homoskedastic
### Heteroskedastic
## Matern 5/2 (n=1000) Log-Normal
### Interpolating
### Homoskedastic
### Heteroskedastic

<!--chapter:end:02-SimulII_Appenix.Rmd-->


# Simulation III Appendix

Placeholder


## Estimated Value Function 
## Matern 5/2 (n=1000)
### Interpolating
### Homoskedastic
### Heteroskedastic
## Matern 3/2 (n=1000)
### Interpolating
### Homoskedastic
### Heteroskedastic
## Matern 5/2; Log-Normal Prior (n=1000)
### Interpolating
### Homoskedastic
### Heteroskedastic

<!--chapter:end:03-SimulIII_Appendix.Rmd-->


```{r, echo=FALSE,message=FALSE}
rm(list=ls(all=TRUE))  # removes all objects from the current workspace

library(LongCART)
library(ggplot2)
library(plotly)#used for plotting
library(kableExtra)
library(reshape2)
library(survey)
library(tableone)
library(labelled)

data("ACTG175")
```
# Case Study 

## Value Surface
```{r,echo=FALSE}
group1=c(2)
group2=c(1)
formula="z~karnof+race+gender+symptom+str2+cd4.0+wtkg"


ACTG175_wide=reshape(ACTG175,idvar = c("pidnum"), timevar = "time", direction = "wide", v.names=c("cd4"))
ACTG175_wide=ACTG175_wide%>%filter(arms%in%c(group1,group2))
ACTG175_wide$z=(ACTG175_wide$arms==2)+0
```

### Estimated Value Function Using Normalized IPW
```{r,echo=FALSE,fig.cap="Estimated value of regime using normalized IPW"}
source("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/Common_Functions.R")
sequence1=seq(50,100,5)
sequence2=seq(200,600,10)
theta=as.matrix(expand.grid(sequence1,sequence2))
colnames(theta)=c("Weight","Baseline_CD4")

proba=compute_probas(formula=formula,Dati=ACTG175_wide,group1=group1,group2=group2,bayes=FALSE,dirichi=NA)
predictions=apply(theta,1,FUN=checki_compliant2d,Dati=ACTG175_wide,group1=group1,group2=group2,weight_estimate=TRUE,proba=proba,normalize=TRUE)

# Surface plot of estimated value function
data_grid2=data.frame(cd4_20week=predictions,
                      weight=theta[,1],
                      cd4_baseline=theta[,2])
plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))


plot_ly(
  x = as.numeric(colnames(plot_matrix2)), 
  y = as.numeric(rownames(plot_matrix2)), 
  z = plot_matrix2) %>% 
  add_surface(opacity=0.8) %>%
  layout(
    scene = list(
      xaxis = list(title = "Weight (Kg)",range=c(50,100)),
      yaxis = list(title = "Baseline CD4", range=c(200,600)),
      zaxis = list(title = "20 Week CD4",range=c(371,410)),
      camera = list(eye = list(x = 1.95, y = -1.25, z = 1.25))
    ))%>%add_trace(x=ACTG175_wide$wtkg, y=ACTG175_wide$cd4.0, z=rep(372,nrow(ACTG175_wide)), type="scatter3d", mode="markers",marker = list(size = 2,opacity=0.8,color="darkblue"))

#Contour plot
# fig=plot_ly(x=~theta[,1],
#             y=~theta[,2],
#             z=~predictions, type="contour",
#             colorscale="Greys",line=list(color="black"),contours = list(showlabels = TRUE))
# fig%>%colorbar(title = "20 Week CD4",titlefont=list(size=25),tickfont=list(size=15))%>%
#   layout(xaxis = list(title = "Baseline Weight (kg)",titlefont=list(size=25),tickfont=list(size=15)),
#          yaxis = list(title = "Baseline CD4",titlefont=list(size=25),tickfont=list(size=15)))
```
### value Surface using MSM

```{r,echo=FALSE,fig.cap="Estimated value surface of regime using quadratic MSM and scatter plot of normalized IPW estimates."}

checki_compliant2d_MSM=function(x,group1,group2,p1){
  x1=x[1]
  x2=x[2]
  subset_ACTG175=ACTG175%>%filter(arms%in%c(group1,group2))
  attach(subset_ACTG175)
  baseline=time==0
  end=time==20
  a=arms[baseline]%in%group1

  #alternative code
  a_regime=(wtkg[baseline]>=x1 & cd4[baseline]>=x2)
  C_d=a_regime==a +0
  detach(subset_ACTG175)
  
  subset_ACTG175$p_d=p1
  subset_ACTG175$C_d=C_d
  subset_ACTG175$x1=x1
  subset_ACTG175$x2=x2
  
  return(cbind(subset_ACTG175[end,c("pidnum","cd4","x1","x2","C_d","p_d")]))
}

MSM_eval=function(x, coefi){
  x1=x[1]
  x2=x[2]
  to_return=coefi[1]+coefi[2]*x1+coefi[3]*x2+coefi[4]*x1^2+coefi[5]*x2^2+coefi[6]*x1*x2
}

sequence1=seq(50,100,10)
sequence2=seq(200,600,100)
theta=as.matrix(expand.grid(sequence1,sequence2))
Max_hist=matrix(NA,nrow=500,ncol=3)

 proba=compute_probas(formula=formula,Dati=ACTG175_wide,group1=c(2),group2=c(1),bayes=FALSE,dirichi=1)

  D1=checki_compliant2d_MSM(x=theta[1,],group1=2,group2=1,p1=proba)
  D2=checki_compliant2d_MSM(x=theta[2,],group1=2,group2=1,p1=proba)
  D3=checki_compliant2d_MSM(x=theta[3,],group1=2,group2=1,p1=proba)
  D4=checki_compliant2d_MSM(x=theta[4,],group1=2,group2=1,p1=proba)
  D5=checki_compliant2d_MSM(x=theta[5,],group1=2,group2=1,p1=proba)
  D6=checki_compliant2d_MSM(x=theta[6,],group1=2,group2=1,p1=proba)
  D7=checki_compliant2d_MSM(x=theta[7,],group1=2,group2=1,p1=proba)
  D8=checki_compliant2d_MSM(x=theta[8,],group1=2,group2=1,p1=proba)
  D9=checki_compliant2d_MSM(x=theta[9,],group1=2,group2=1,p1=proba)
  D10=checki_compliant2d_MSM(x=theta[10,],group1=2,group2=1,p1=proba)
  D11=checki_compliant2d_MSM(x=theta[11,],group1=2,group2=1,p1=proba)
  D12=checki_compliant2d_MSM(x=theta[12,],group1=2,group2=1,p1=proba)
  D13=checki_compliant2d_MSM(x=theta[13,],group1=2,group2=1,p1=proba)
  D14=checki_compliant2d_MSM(x=theta[14,],group1=2,group2=1,p1=proba)
  D15=checki_compliant2d_MSM(x=theta[15,],group1=2,group2=1,p1=proba)
  D16=checki_compliant2d_MSM(x=theta[16,],group1=2,group2=1,p1=proba)
  D17=checki_compliant2d_MSM(x=theta[17,],group1=2,group2=1,p1=proba)
  D18=checki_compliant2d_MSM(x=theta[18,],group1=2,group2=1,p1=proba)
  D19=checki_compliant2d_MSM(x=theta[19,],group1=2,group2=1,p1=proba)
  D20=checki_compliant2d_MSM(x=theta[20,],group1=2,group2=1,p1=proba)
  D21=checki_compliant2d_MSM(x=theta[21,],group1=2,group2=1,p1=proba)
  D22=checki_compliant2d_MSM(x=theta[22,],group1=2,group2=1,p1=proba)
  D23=checki_compliant2d_MSM(x=theta[23,],group1=2,group2=1,p1=proba)
  D24=checki_compliant2d_MSM(x=theta[24,],group1=2,group2=1,p1=proba)
  D25=checki_compliant2d_MSM(x=theta[25,],group1=2,group2=1,p1=proba)
  D26=checki_compliant2d_MSM(x=theta[26,],group1=2,group2=1,p1=proba)
  D27=checki_compliant2d_MSM(x=theta[27,],group1=2,group2=1,p1=proba)
  D28=checki_compliant2d_MSM(x=theta[28,],group1=2,group2=1,p1=proba)
  D29=checki_compliant2d_MSM(x=theta[29,],group1=2,group2=1,p1=proba)
  D30=checki_compliant2d_MSM(x=theta[30,],group1=2,group2=1,p1=proba)
  
  Augmented_Data=rbind(D1,D2,D3,D4,D5,D6,D7,D8,D9,D10,D11,D12,D13,D14,D12,D16,D17,D18,D19,D20,D21,D22,D23,D24,D25,D26,D27,D28,D29,D30)
  
  Augmented_Data$weight= Augmented_Data$C_d/Augmented_Data$p_d
  
  coefi=coef(lm(cd4~x1+x2+I(x1^2)+I(x2^2)+x1:x2 ,data=Augmented_Data, weights = weight))


  
#------------------------  
sequence1=seq(50,100,1)
sequence2=seq(200,600,10)
evali=as.matrix(expand.grid(sequence1,sequence2))
colnames(theta)=c("Weight","Baseline_CD4")

z1=apply(evali,1,FUN=MSM_eval,coefi=coefi)
z2=apply(evali,1,FUN=checki_compliant2d,Dati=ACTG175_wide,group1=c(2),group2=c(1),
                                        weight_estimate=TRUE,proba=proba,normalize=TRUE)

Data1=data.frame(z=z1,y=evali[,2],x=evali[,1],groupy=1)
Data2=data.frame(z=z2,y=evali[,2],x=evali[,1],groupy=2)
Final_Data=rbind(Data1,Data2)
coly=c("MSM","IPW Grid")

# plot_ly(x=Final_Data$x, y=Final_Data$y, z=Final_Data$z, type="scatter3d", mode="markers",color=coly[Final_Data$groupy],colors=c("blue","red"),marker = list(size = 2))%>%
#   layout(scene = list(xaxis = list(title = "Baseline Weight",zerolinecolor = '#ffff'),
#                  yaxis = list(title = "Baseline CD4"),
#                  zaxis = list(title = "20 Week CD4")))


data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
                      weight=Final_Data$x[Final_Data$groupy==1],
                      cd4_baseline=Final_Data$y[Final_Data$groupy==1])
plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))

plot_ly(
  x = as.numeric(colnames(plot_matrix2)), 
  y = as.numeric(rownames(plot_matrix2)), 
  z = plot_matrix2) %>% 
  add_surface(opacity=0.8) %>%
  layout(
    scene = list(
      xaxis = list(title = "Weight (Kg)",range=c(50,100)),
      yaxis = list(title = "Baseline CD4", range=c(200,600)),
      zaxis = list(title = "20 Week CD4",range=c(371,410)),
      camera = list(eye = list(x = 1.95, y = -1.25, z = 1.25))
    ))%>%add_trace(x=Final_Data$x[Final_Data$groupy==2], y=Final_Data$y[Final_Data$groupy==2], z=Final_Data$z[Final_Data$groupy==2], type="scatter3d", mode="markers",marker = list(size = 2,opacity=0.8,color="darkred"))

```
## Matern 5/2 GP Graphics

### Interpolating GP 

```{r,echo=FALSE,fig.cap="Estimated value of regime using interpolating GP after an additional 25 sampled points"}
theta=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue/theta_21TRUETRUE.csv")
xhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue/xhist_21TRUeTRUE.csv")
yhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue/yhist_21TRUETRUE.csv")
Final_Data=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue/Final_Data_21TRUETRUE.csv")


data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
                      weight=Final_Data$x[Final_Data$groupy==1],
                      cd4_baseline=Final_Data$y[Final_Data$groupy==1])
plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))


plot_ly(
  x = as.numeric(colnames(plot_matrix2)), 
  y = as.numeric(rownames(plot_matrix2)), 
  z = plot_matrix2) %>% 
  add_surface(opacity=0.8)%>%
  layout( scene=list(xaxis = list(title="Baseline Weight (kg)"),
                    yaxis = list(title="Baseline CD4"),
                    zaxis =  list(title="20 Week CD4"))) %>%
  add_trace(x=Final_Data$x[Final_Data$groupy==2], y=Final_Data$y[Final_Data$groupy==2],                  z=Final_Data$z[Final_Data$groupy==2],type="scatter3d", mode="markers",marker = list(size = 2,opacity=0.8,color="darkblue",size=10))



#Contour Plot
# data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
#                       weight=Final_Data$x[Final_Data$groupy==1],
#                       cd4_baseline=Final_Data$y[Final_Data$groupy==1])
# plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))

# fig=plot_ly(x=~Final_Data$x[Final_Data$groupy==1],
#             y=~Final_Data$y[Final_Data$groupy==1],
#             z=~Final_Data$z[Final_Data$groupy==1], type="contour",
#             colorscale="Greys",line=list(color="black"), contours = list(showlabels = TRUE))
# fig%>%colorbar(title = "20 Week \n CD4",titlefont=list(size=25),tickfont=list(size=15))%>%
#   layout(
#          xaxis = list(title = "Baseline Weight (kg)",titlefont=list(size=25),tickfont=list(size=15)),
#          yaxis = list(title = "Baseline CD4",titlefont=list(size=25),tickfont=list(size=15)))%>%
#   add_trace(x=~Final_Data$x[Final_Data$groupy==2],y=~Final_Data$y[Final_Data$groupy==2],
#             type = "scatter", mode="markers", marker=list(color="grey"),inherit=FALSE)


```

### Homoskedastic GP

```{r, echo=FALSE,fig.cap="Estimated value of regime using homoskedastic GP after an additional 25 sampled points"}
theta=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue/theta_Homo_21TRUETRUE.csv")
xhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue/xhist_Homo_21TRUETRUE.csv")
yhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue/yhist_Homo_21TRUETRUE.csv")
Final_Data=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue/Final_Data_Homo_21TRUETRUE.csv")


data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
                      weight=Final_Data$x[Final_Data$groupy==1],
                      cd4_baseline=Final_Data$y[Final_Data$groupy==1])
plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))


plot_ly(
  x = as.numeric(colnames(plot_matrix2)), 
  y = as.numeric(rownames(plot_matrix2)), 
  z = plot_matrix2) %>% 
  add_surface(opacity=0.8)%>%
  layout(
         scene=list(xaxis = list(title="Baseline Weight (kg)"),
                    yaxis = list(title="Baseline CD4"),
                    zaxis =  list(title="20 Week CD4"))) %>%
  add_trace(x=Final_Data$x[Final_Data$groupy==2], y=Final_Data$y[Final_Data$groupy==2],                  z=Final_Data$z[Final_Data$groupy==2],type="scatter3d", mode="markers",marker = list(size = 2,opacity=0.8,color="darkblue",size=10))



#Contour Plot
# data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
#                       weight=Final_Data$x[Final_Data$groupy==1],
#                       cd4_baseline=Final_Data$y[Final_Data$groupy==1])
# plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))


# fig=plot_ly(x=~Final_Data$x[Final_Data$groupy==1],
#             y=~Final_Data$y[Final_Data$groupy==1],
#             z=~Final_Data$z[Final_Data$groupy==1], type="contour",
#             colorscale="Greys",line=list(color="black"), contours = list(showlabels = TRUE))
# fig%>%colorbar(title = "20 Week \n CD4",titlefont=list(size=25),tickfont=list(size=15))%>%
#   layout(xaxis = list(title = "Baseline Weight (kg)",titlefont=list(size=25),tickfont=list(size=15)),
#          yaxis = list(title = "Baseline CD4",titlefont=list(size=25),tickfont=list(size=15)))%>%
#   add_trace(x=~Final_Data$x[Final_Data$groupy==2],y=~Final_Data$y[Final_Data$groupy==2],
#             type = "scatter", mode="markers", marker=list(color="grey"),inherit=FALSE)

```


### Heteroskedstic GP

```{r,echo=FALSE,fig.cap="Estimated value of regime using heteroskedastic GP after an additional 25 sampled points"}
theta=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue/theta_Hetero_21TRUETRUE.csv")
xhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue/xhist_Hetero_21TRUETRUE.csv")
yhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue/yhist_Hetero_21TRUETRUE.csv")
Final_Data=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue/Final_Data_Hetero_21TRUETRUE.csv")


data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
                      weight=Final_Data$x[Final_Data$groupy==1],
                      cd4_baseline=Final_Data$y[Final_Data$groupy==1])
plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week",marker = list(size = 2,opacity=0.8,color="darkblue",size=10)))


plot_ly(
  x = as.numeric(colnames(plot_matrix2)), 
  y = as.numeric(rownames(plot_matrix2)), 
  z = plot_matrix2) %>% 
  add_surface(opacity=0.8)%>%
  layout(
         scene=list(xaxis = list(title="Baseline Weight (kg)"),
                    yaxis = list(title="Baseline CD4"),
                    zaxis =  list(title="20 Week CD4"))) %>%
  add_trace(x=Final_Data$x[Final_Data$groupy==2], y=Final_Data$y[Final_Data$groupy==2],                  z=Final_Data$z[Final_Data$groupy==2],type="scatter3d", mode="markers",marker = list(size = 2,opacity=0.8,color="darkblue",size=10))

# Contour Plot
# fig=plot_ly(x=~Final_Data$x[Final_Data$groupy==1],
#             y=~Final_Data$y[Final_Data$groupy==1],
#             z=~Final_Data$z[Final_Data$groupy==1], type="contour",
#             colorscale="Greys",line=list(color="black"), contours = list(showlabels = TRUE))
# fig%>%colorbar(title = "20 Week \n CD4",titlefont=list(size=25),tickfont=list(size=15))%>%
#   layout(
#          xaxis = list(title = "Baseline Weight (kg)",titlefont=list(size=25),tickfont=list(size=15)),
#          yaxis = list(title = "Baseline CD4",titlefont=list(size=25),tickfont=list(size=15)))%>%
#   add_trace(x=~Final_Data$x[Final_Data$groupy==2],y=~Final_Data$y[Final_Data$groupy==2],
#             type = "scatter", mode="markers", marker=list(color="grey"),inherit=FALSE)
```

## Matern 3/2 GP Graphics

### Interpolating GP
```{r,echo=FALSE,fig.cap="Estimated value of regime using interpolating GP after an additional 25 sampled points"}
theta=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_cov32/theta_21TRUETRUE_1.csv")
xhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_cov32/xhist_21TRUETRUE_1.csv")
yhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_cov32/yhist_21TRUETRUE_1.csv")
Final_Data=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_cov32/Final_Data_21TRUETRUE_1.csv")


data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
                      weight=Final_Data$x[Final_Data$groupy==1],
                      cd4_baseline=Final_Data$y[Final_Data$groupy==1])
plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))


plot_ly(
  x = as.numeric(colnames(plot_matrix2)), 
  y = as.numeric(rownames(plot_matrix2)), 
  z = plot_matrix2) %>% 
  add_surface(opacity=0.8)%>%
  layout( scene=list(xaxis = list(title="Baseline Weight (kg)"),
                    yaxis = list(title="Baseline CD4"),
                    zaxis =  list(title="20 Week CD4"))) %>%
  add_trace(x=Final_Data$x[Final_Data$groupy==2], y=Final_Data$y[Final_Data$groupy==2],                  z=Final_Data$z[Final_Data$groupy==2],type="scatter3d", mode="markers",marker = list(size = 2,opacity=0.8,color="darkblue",size=10))



#Contour Plot
# data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
#                       weight=Final_Data$x[Final_Data$groupy==1],
#                       cd4_baseline=Final_Data$y[Final_Data$groupy==1])
# plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))
# fig=plot_ly(x=~Final_Data$x[Final_Data$groupy==1],
#             y=~Final_Data$y[Final_Data$groupy==1],
#             z=~Final_Data$z[Final_Data$groupy==1], type="contour",
#             colorscale="Greys",line=list(color="black"), contours = list(showlabels = TRUE))
# fig%>%colorbar(title = "20 Week \n CD4",titlefont=list(size=25),tickfont=list(size=15))%>%
#   layout(
#          xaxis = list(title = "Baseline Weight (kg)",titlefont=list(size=25),tickfont=list(size=15)),
#          yaxis = list(title = "Baseline CD4",titlefont=list(size=25),tickfont=list(size=15)))%>%
#   add_trace(x=~Final_Data$x[Final_Data$groupy==2],y=~Final_Data$y[Final_Data$groupy==2],
#             type = "scatter", mode="markers", marker=list(color="grey"),inherit=FALSE)
```

### Homoskedastic GP

```{r, echo=FALSE,fig.cap="Estimated value of regime using homoskedastic GP after an additional 25 sampled points"}
theta=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_cov32/theta_Homo_21TRUETRUE_1.csv")
xhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_cov32/xhist_Homo_21TRUETRUE_1.csv")
yhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_cov32/yhist_Homo_21TRUETRUE_1.csv")
Final_Data=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_cov32/Final_Data_Homo_21TRUETRUE_1.csv")


data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
                      weight=Final_Data$x[Final_Data$groupy==1],
                      cd4_baseline=Final_Data$y[Final_Data$groupy==1])
plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))


plot_ly(
  x = as.numeric(colnames(plot_matrix2)), 
  y = as.numeric(rownames(plot_matrix2)), 
  z = plot_matrix2) %>% 
  add_surface(opacity=0.8)%>%
  layout(
         scene=list(xaxis = list(title="Baseline Weight (kg)"),
                    yaxis = list(title="Baseline CD4"),
                    zaxis =  list(title="20 Week CD4"))) %>%
  add_trace(x=Final_Data$x[Final_Data$groupy==2], y=Final_Data$y[Final_Data$groupy==2],                  z=Final_Data$z[Final_Data$groupy==2],type="scatter3d", mode="markers",marker = list(size = 2,opacity=0.8,color="darkblue",size=10))



#Contour Plot
# data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
#                       weight=Final_Data$x[Final_Data$groupy==1],
#                       cd4_baseline=Final_Data$y[Final_Data$groupy==1])
# plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))
# fig=plot_ly(x=~Final_Data$x[Final_Data$groupy==1],
#             y=~Final_Data$y[Final_Data$groupy==1],
#             z=~Final_Data$z[Final_Data$groupy==1], type="contour",
#             colorscale="Greys",line=list(color="black"), contours = list(showlabels = TRUE))
# fig%>%colorbar(title = "20 Week \n CD4",titlefont=list(size=25),tickfont=list(size=15))%>%
#   layout(xaxis = list(title = "Baseline Weight (kg)",titlefont=list(size=25),tickfont=list(size=15)),
#          yaxis = list(title = "Baseline CD4",titlefont=list(size=25),tickfont=list(size=15)))%>%
#   add_trace(x=~Final_Data$x[Final_Data$groupy==2],y=~Final_Data$y[Final_Data$groupy==2],
#             type = "scatter", mode="markers", marker=list(color="grey"),inherit=FALSE)

```


### Heteroskedastic GP 

```{r, echo=FALSE,fig.cap="Estimated value of regime using homoskedastic GP after an additional 25 sampled points"}
theta=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_cov32/theta_Hetero_21TRUETRUE_1.csv")
xhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_cov32/xhist_Hetero_21TRUETRUE_1.csv")
yhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_cov32/yhist_Hetero_21TRUETRUE_1.csv")
Final_Data=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_cov32/Final_Data_Hetero_21TRUETRUE_1.csv")


data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
                      weight=Final_Data$x[Final_Data$groupy==1],
                      cd4_baseline=Final_Data$y[Final_Data$groupy==1])
plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))


plot_ly(
  x = as.numeric(colnames(plot_matrix2)), 
  y = as.numeric(rownames(plot_matrix2)), 
  z = plot_matrix2) %>% 
  add_surface(opacity=0.8)%>%
  layout(
         scene=list(xaxis = list(title="Baseline Weight (kg)"),
                    yaxis = list(title="Baseline CD4"),
                    zaxis =  list(title="20 Week CD4"))) %>%
  add_trace(x=Final_Data$x[Final_Data$groupy==2], y=Final_Data$y[Final_Data$groupy==2],                  z=Final_Data$z[Final_Data$groupy==2],type="scatter3d", mode="markers",marker = list(size = 2,opacity=0.8,color="darkblue",size=10))


#Contour Plot
# data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
#                       weight=Final_Data$x[Final_Data$groupy==1],
#                       cd4_baseline=Final_Data$y[Final_Data$groupy==1])
# plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))
# fig=plot_ly(x=~Final_Data$x[Final_Data$groupy==1],
#             y=~Final_Data$y[Final_Data$groupy==1],
#             z=~Final_Data$z[Final_Data$groupy==1], type="contour",
#             colorscale="Greys",line=list(color="black"), contours = list(showlabels = TRUE))
# fig%>%colorbar(title = "20 Week \n CD4",titlefont=list(size=25),tickfont=list(size=15))%>%
#   layout(xaxis = list(title = "Baseline Weight (kg)",titlefont=list(size=25),tickfont=list(size=15)),
#          yaxis = list(title = "Baseline CD4",titlefont=list(size=25),tickfont=list(size=15)))%>%
#   add_trace(x=~Final_Data$x[Final_Data$groupy==2],y=~Final_Data$y[Final_Data$groupy==2],
#             type = "scatter", mode="markers", marker=list(color="grey"),inherit=FALSE)

```

## Matern 5/2 Covariance; Log Normal Prior


### Interpolating GP
```{r,echo=FALSE,fig.cap="Estimated value of regime using interpolating GP after an additional 25 sampled points"}
theta=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_prior/theta_21TRUETRUE_31.csv")
xhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_prior/xhist_21TRUETRUE_31.csv")
yhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_prior/yhist_21TRUETRUE_31.csv")
Final_Data=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_prior/Final_Data_21TRUETRUE_31.csv")


data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
                      weight=Final_Data$x[Final_Data$groupy==1],
                      cd4_baseline=Final_Data$y[Final_Data$groupy==1])
plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))


plot_ly(
  x = as.numeric(colnames(plot_matrix2)), 
  y = as.numeric(rownames(plot_matrix2)), 
  z = plot_matrix2) %>% 
  add_surface(opacity=0.8)%>%
  layout( scene=list(xaxis = list(title="Baseline Weight (kg)"),
                    yaxis = list(title="Baseline CD4"),
                    zaxis =  list(title="20 Week CD4"))) %>%
  add_trace(x=Final_Data$x[Final_Data$groupy==2], y=Final_Data$y[Final_Data$groupy==2],                  z=Final_Data$z[Final_Data$groupy==2],type="scatter3d", mode="markers",marker = list(size = 2,opacity=0.8,color="darkblue",size=10))



#Contour Plot
data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
                      weight=Final_Data$x[Final_Data$groupy==1],
                      cd4_baseline=Final_Data$y[Final_Data$groupy==1])
plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))
fig=plot_ly(x=~Final_Data$x[Final_Data$groupy==1],
            y=~Final_Data$y[Final_Data$groupy==1],
            z=~Final_Data$z[Final_Data$groupy==1], type="contour",
            colorscale="Greys",line=list(color="black"), contours = list(showlabels = TRUE))
fig%>%colorbar(title = "20 Week \n CD4",titlefont=list(size=25),tickfont=list(size=15))%>%
  layout(
         xaxis = list(title = "Baseline Weight (kg)",titlefont=list(size=25),tickfont=list(size=15)),
         yaxis = list(title = "Baseline CD4",titlefont=list(size=25),tickfont=list(size=15)))%>%
  add_trace(x=~Final_Data$x[Final_Data$groupy==2],y=~Final_Data$y[Final_Data$groupy==2],
            type = "scatter", mode="markers", marker=list(color="grey"),inherit=FALSE)
```

### Homoskedastic GP

```{r, echo=FALSE,fig.cap="Estimated value of regime using homoskedastic GP after an additional 25 sampled points"}
theta=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_prior/theta_Homo_21TRUETRUE_31.csv")
xhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_prior/xhist_Homo_21TRUETRUE_31.csv")
yhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_prior/yhist_Homo_21TRUETRUE_31.csv")
Final_Data=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_prior/Final_Data_Homo_21TRUETRUE_31.csv")


data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
                      weight=Final_Data$x[Final_Data$groupy==1],
                      cd4_baseline=Final_Data$y[Final_Data$groupy==1])
plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))


plot_ly(
  x = as.numeric(colnames(plot_matrix2)), 
  y = as.numeric(rownames(plot_matrix2)), 
  z = plot_matrix2) %>% 
  add_surface(opacity=0.8)%>%
  layout(
         scene=list(xaxis = list(title="Baseline Weight (kg)"),
                    yaxis = list(title="Baseline CD4"),
                    zaxis =  list(title="20 Week CD4"))) %>%
  add_trace(x=Final_Data$x[Final_Data$groupy==2], y=Final_Data$y[Final_Data$groupy==2],                  z=Final_Data$z[Final_Data$groupy==2],type="scatter3d", mode="markers",marker = list(size = 2,opacity=0.8,color="darkblue",size=10))



#Contour Plot
data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
                      weight=Final_Data$x[Final_Data$groupy==1],
                      cd4_baseline=Final_Data$y[Final_Data$groupy==1])
plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))
fig=plot_ly(x=~Final_Data$x[Final_Data$groupy==1],
            y=~Final_Data$y[Final_Data$groupy==1],
            z=~Final_Data$z[Final_Data$groupy==1], type="contour",
            colorscale="Greys",line=list(color="black"), contours = list(showlabels = TRUE))
fig%>%colorbar(title = "20 Week \n CD4",titlefont=list(size=25),tickfont=list(size=15))%>%
  layout(xaxis = list(title = "Baseline Weight (kg)",titlefont=list(size=25),tickfont=list(size=15)),
         yaxis = list(title = "Baseline CD4",titlefont=list(size=25),tickfont=list(size=15)))%>%
  add_trace(x=~Final_Data$x[Final_Data$groupy==2],y=~Final_Data$y[Final_Data$groupy==2],
            type = "scatter", mode="markers", marker=list(color="grey"),inherit=FALSE)

```




### Heteroskedastic GP 

```{r, echo=FALSE,fig.cap="Estimated value of regime using homoskedastic GP after an additional 25 sampled points"}
theta=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_prior/theta_Hetero_21TRUETRUE_31.csv")
xhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_prior/xhist_Hetero_21TRUETRUE_31.csv")
yhist=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_prior/yhist_Hetero_21TRUETRUE_31.csv")
Final_Data=read.csv("C:/Users/Administrator/Dropbox/Daniel_PhD_Research/Objective II/Analysis/21_WeightTrue_prior/Final_Data_Hetero_21TRUETRUE_31.csv")


data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
                      weight=Final_Data$x[Final_Data$groupy==1],
                      cd4_baseline=Final_Data$y[Final_Data$groupy==1])
plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))


plot_ly(
  x = as.numeric(colnames(plot_matrix2)), 
  y = as.numeric(rownames(plot_matrix2)), 
  z = plot_matrix2) %>% 
  add_surface(opacity=0.8)%>%
  layout(
         scene=list(xaxis = list(title="Baseline Weight (kg)"),
                    yaxis = list(title="Baseline CD4"),
                    zaxis =  list(title="20 Week CD4"))) %>%
  add_trace(x=Final_Data$x[Final_Data$groupy==2], y=Final_Data$y[Final_Data$groupy==2],                  z=Final_Data$z[Final_Data$groupy==2],type="scatter3d", mode="markers",marker = list(size = 2,opacity=0.8,color="darkblue",size=10))


#Contour Plot
data_grid2=data.frame(cd4_20week=Final_Data$z[Final_Data$groupy==1],
                      weight=Final_Data$x[Final_Data$groupy==1],
                      cd4_baseline=Final_Data$y[Final_Data$groupy==1])
plot_matrix2 <- t(acast(data_grid2, weight~ cd4_baseline, value.var="cd4_20week"))
fig=plot_ly(x=~Final_Data$x[Final_Data$groupy==1],
            y=~Final_Data$y[Final_Data$groupy==1],
            z=~Final_Data$z[Final_Data$groupy==1], type="contour",
            colorscale="Greys",line=list(color="black"), contours = list(showlabels = TRUE))
fig%>%colorbar(title = "20 Week \n CD4",titlefont=list(size=25),tickfont=list(size=15))%>%
  layout(xaxis = list(title = "Baseline Weight (kg)",titlefont=list(size=25),tickfont=list(size=15)),
         yaxis = list(title = "Baseline CD4",titlefont=list(size=25),tickfont=list(size=15)))%>%
  add_trace(x=~Final_Data$x[Final_Data$groupy==2],y=~Final_Data$y[Final_Data$groupy==2],
            type = "scatter", mode="markers", marker=list(color="grey"),inherit=FALSE)

```



























<!--chapter:end:04-Case_Study.Rmd-->

